### 2012-12-04 inst/examples/policycosts/quick_examples.Rmd

Actually, we'll want to draw these from the table in figure4 data at different levels.  
Ideally we can draw the policy out rather than running that again.

```{r apples}
apples <- c(L2=1.034, L1=1.724, free_decrease=1.724, fixed=8.276, free_increase=1.724)
````

@@

Solve the policy cost for the specified penalty function.

@@

Calculate statistics of the kind used in figure 4.

```{r}
dt[,var(harvest), by=penalty_fn]
dt[,acf(harvest, lag.max=1, plot=F)$acf[2], by=penalty_fn]
```

>>>>

```{r apples}
apples <- c(L2=1.034, L1=1.724, free_decrease=1.724, fixed=8.276, free_increase=1.724)
xtable(apples)
````

@@

Solve the policy cost for the specified penalty function

@@
